Machine Learning Model for Agricultural Data Applications

### 2021-03-25 chapters/methods.tex
Method Dev

\todo{In addition, extract questions that go into a table. Justify why you have selected the sections and reference the Literature review. Maybe not relevant to my work.}
Data Science is a subset of Computer Science and Mathematics. This subset introduces a new paradigm which creates algorithms for computers and robots. It combines statistics with Computer Science. Data Science also involves the use of machine learning algorithms for prediction.

@@

\subsection{Supervised Learning} %Dev Later
Supervised learning is further categorized as  either \textbf{\textit{Regression}} or \textbf{\textit{Classification.}} The main difference between Regression and Classification is that the output variable in Regression is numerical while that for Classification is categorical. In other words, Regression predicts a quantity while  Classification predicts a label.

@@

@@

\subsection{Unsupervised Learning}
%leave AS-_is

@@

\section{Neural Networks}
A neural network is a collection of algorithms that, through a mechanism that mimics the way the human brain works, aim to identify fundamental connections in a data set \cite{jain1999recurrent}.  Neural networks, in this context, apply to neuron frameworks, either biological or artificial in nature. Neural networks may respond to evolving inputs, so the network delivers the best possible outcome without the performance parameters having to be revamped. In the development of trading systems, the notion of neural networks, which has its origins in artificial intelligence, is rapidly gaining prominence.\citealp*{krose1993introduction}.

@@

\section{Recurring Neural Network}

>>>>

\todo{In addition, extract questions that go into a table. Justify why you have selected the sections and reference the Literature review. Maybe not relevant to my work.}

Data Science is a subset of Computer Science and Mathematics. This subset introduces a new paradigm which creates algorithms for computers and robots. Data Science also involves the use of machine learning algorithms for prediction.

The foundation of every current field of science is mathematics. Almost all data science methods have a strong mathematical underpinning, like machine learning.
It comes as no surprise that to work as a top data scientist, you would completely need all the other beads of expertise-programming ability, some volume of business intelligence, and your unique analytical and curious mentality-about the data. But learning the machinery under the hood is still worth it, instead of just being the guy behind the wheel with no understanding of the car. A good awareness of the mathematical machinery behind the trendy algorithms would also give you an advantage over your colleagues.

\section{Machine Learning}

@@

\subsection{Supervised Learning}
Supervised learning is essentially a formalization of the notion of learning from formerly supervised fields of learning. The learner (usually, a computer programme) is presented with two data sets, a training set and a test set during supervised learning. The idea is to set the learner's training set test to learn 'from a set of classified examples in the training set such that unlabeled examples can be defined with the greatest expected precision in the test set. That is, the learner's goal is to create a law, a programme, or a process that classifies new examples by evaluating examples that already have a class \cite{learned2014introduction}

Supervised learning is further categorized as  either \textbf{\textit{Regression}} or \textbf{\textit{Classification.}} The main difference between Regression and Classification is that the output variable in Regression is numerical while that for Classification is categorical. In other words, Regression predicts a quantity while  Classification predicts a label.

@@

A natural extension of multiple linear regression is multivariate linear regression in that both methods aim to explain hypothetical linear correlations between some variables of outputs and inputs. Multiple regression is focused on the analysis of the degree to which a set of "i" input variables X= (X1,Xi) influences the behaviour of a single output variable Y. The multivariate regression has "o" output variables Y= (Y1,Yo), each of which can be affected by precisely the same range of X= (X1,Xi) inputs.\cite{izenman2013multivariate}

@@

\subsection{Unsupervised Learning}
Unsupervised learning is a category of ML methods that work in the dataset of unlabeled data in order to explore frameworks or trends. New paradigms for unsupervised learning (as such-called self-supervised learning) have also been introduced to manipulate multiple labels that are readily accessible to learn general purpose characteristics in addition to or within visual data.\cite{dayan1999unsupervised}
Unsupervised learning explores how models should learn in a way that illustrates the mathematical form of the overall input sequence set to describe individual input sequence. In comparison to supervised learning or reinforcement learning, each feedback is not correlated with specific goal outcomes or environmental assessments; instead, the unsupervised learning incorporates previous prejudices as to what elements of the input system can be reflected in the output.\cite{dayan1999unsupervised}

@@

\section{Neural Networks}
A neural network is a collection of algorithms that, through a mechanism that mimics the way the human brain works, aim to identify fundamental connections in a data set \cite{jain1999recurrent}.  Neural networks, in this context, apply to neuron frameworks, either biological or artificial in nature.

\subsection{Biological Neural Network}
Neural networks may respond to evolving inputs, so the network delivers the best possible outcome without the performance parameters having to be revamped. In the development of trading systems, the notion of neural networks, which has its origins in artificial intelligence, is rapidly gaining prominence.\citealp*{krose1993introduction}.

@@

\subsection{Artificial Neural Network}

To be developed.

\section{Deep Neural Network}
